Methods for Analyzing Models of\\ Rod-Shaped Bacteria

### 2025-09-20 paper/main.tex
cleanup
use correct images
insert description for figure

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000000.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000001.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000002.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000003.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000004.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000005.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{F}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000005.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{G}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000005.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{H}};
    \end{tikzonimage}%
    \caption{TODO}
    \label{fig:likelihood-profiles-comparison-with-division}
\end{figure}

@@

%###################################################################################################
% EXCLUDE THIS FOR NOW
% \section{Plastic Deformations}
% 
% \begin{figure}
%     \centering
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_amir/0000000023.png}\\
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_amir/angles.pdf}
%     \includegraphics[width=0.49\textwidth]
%         {docs/source/_static/scripts/crm_amir/endpoints.pdf}
%     \caption{TODO}
%     \label{fig:amir}
% \end{figure}

>>>>

\begin{figure}
    \centering
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000000.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{A}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000001.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{B}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000002.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{C}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000003.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{D}};
    \end{tikzonimage}\\
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000004.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{E}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000005.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{F}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000006.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{G}};
    \end{tikzonimage}%
    \begin{tikzonimage}[width=0.25\textwidth]
        {figures/crm_divide/profiles/profile-000007.png}%
        \node at (0.15, 0.85)[anchor=north west, rectangle, draw, black, minimum width=15pt, minimum height=15pt]{\textbf{H}};
    \end{tikzonimage}%
    \caption{
        Likelihood profiles of every estimated parameter.
        (A-D) Division Lengths of initially placed cells.
        (E-H) Growth rates of daughter cells.
        The growth rates diplay larger values of noise within their profiles compared to the
        division lengths.
        \textbf{TODO possibly extend this description?}
    }
    \label{fig:likelihood-profiles-comparison-with-division}
\end{figure}

@@
